Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-11-07 edubots_surveys.Rnw
typo

The introduction of new technologies in the classroom, to be successful, involves extra teacher training, devising methods for enhancing student engagement with the new technology and in deed acquiring new skills by both. Some technologies are readily adopted, but others require longer time for full adoption. In most cases, the magnitude of the uptake of the new technology impinges on the collaboration of all the parties using it. Hence, examining the users’ opinions and 
is an important first step in boosting this collaboration and reaping the benefits of the technology.  Recently, a surge in the use of synchronous instant messaging tools in higher education such as WhatsApp, Telegram and Facebook Messenger took place. Some messaging applications have built in chatbots that are able to support a synchronous conversation between the different parties \cite{differ.chat}, while other chatbots are developed as standalone systems and can possibly be attached to a messaging application using an API (Application Program Interface).

>>>>

The introduction of new technologies in the classroom, to be successful, involves extra teacher training, devising methods for enhancing student engagement with the new technology and indeed acquiring new skills by both. Some technologies are readily adopted, but others require longer time for full adoption. In most cases, the magnitude of the uptake of the new technology impinges on the collaboration of all the parties using it. Hence, examining the users’ opinions and 
is an important first step in boosting this collaboration and reaping the benefits of the technology.  Recently, a surge in the use of synchronous instant messaging tools in higher education such as WhatsApp, Telegram and Facebook Messenger took place. Some messaging applications have built in chatbots that are able to support a synchronous conversation between the different parties \cite{differ.chat}, while other chatbots are developed as standalone systems and can possibly be attached to a messaging application using an API (Application Program Interface).
